A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-11-05 paper/paper.tex
Citation discrete fibrations

A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category. As such, it lives on the indexed side of the correspondence, opposing on the fibered side to \emph{discrete Grothendieck fibrations}~\cite{FIND-A-CITATION}. However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence. Indeed, when the indexing category is \emph{direct}, i.e. with a downwards-well-founded collection of non-identity morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an \emph{indexed presentation} of the presheaf over the direct category.

>>>>

A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category. As such, it lives on the indexed side of the correspondence, opposing on the fibered side to \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}. However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence. Indeed, when the indexing category is \emph{direct}, i.e. with a downwards-well-founded collection of non-identity morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an \emph{indexed presentation} of the presheaf over the direct category.
